Fast Mini-Batch MCMC for Big Data Bayesian Posterior Inference

### 2016-05-12 nips_2016.tex
Updated writeup to include new list of references

>>>>

Some additional references to use:

\begin{itemize}
    \item \cite{icml2014c1_bardenet14} (ICML 2014) I think we definitely want to consider this. It
    seems to be ``an alternative to the Cutting the MH budget approach'' and so it might also be
    considered as a direct competitor.
    \item \cite{conf/icml/AhnBW12} (ICML 2012) is the ``successor'' to Stochastic Gradient Langevin
    Dynamics.
    \item \cite{conf/uai/MaclaurinA14} (UAI 2014) seems like it would be interesting to state its
    limitations.
    \item \cite{mcmc_hamiltonian_2010} is a long paper and is written like a chapter in a textbook,
    so it's for pedagogical reasons. It describes MCMC with Hamiltonian dynamics. It is useful to
    gain some background on a lot of the HMC-related papers that have come since its publication
    (2010).
    \item \cite{stochastic_thermostats_2014} (NIPS 2014) might be considered as a ``competitor''
    though only for HMC cases.
    \item \cite{sgmcmc_2015} (NIPS 2015) might want to give this a mention, where it would fit in
    their recipe.
\end{itemize}
